\documentclass[12pt]{article}\begin{document}\title{The Brandiss Class and Package}\author{Mario O.~Bourgoin}\date{May 5, 2004}\maketitle\begin{abstract}  The brandiss \LaTeX\ class and the associated package are intended  to ease creating a dissertation in \LaTeX\ that meets the formatting  requirements of the Brandeis Graduate School of Arts and Sciences,  including those for on-line submission.\end{abstract}\section{Introduction}The \emph{brandiss} \LaTeX\ class and the brandiss \LaTeX\ package areintended to ease creating a dissertation in \LaTeX\ that meets theformatting requirements of the Brandeis Graduate School of Arts andSciences (GSAS), including those for on-line submission.  The classextends the \emph{amsbook} class of the AMS by setting the defaultfont size to 12 point, one-sided pagination, GSAS specified minimummargins, center footer page numbering, and PDF compression level 0.The package adds commands and environments for formatting the frontpages of the dissertation.\section{Using The Brandiss Class and Package}To use the class, copy the brandisssample.tex file and modify it toinclude your dissertation.  If you want to have a hyperlinked documentand are experienced enough with \LaTeX\ to solve your own problems,copy the brandisshyper.tex file and modify it to include yourdissertation.  If you want to create your own dissertation formatstarting from the front pages defined for the brandiss class, you canuse the brandiss package.  In this case, the brandiss class definitioncan help guide you towards the means of creating your format.\section{Class and Package Options}The brandiss class has all of the options of the amsbook class, andtwo more: online vs.~printed and uncompressed vs.~compressed.  The``online'' and ``printed'' options are passed to the brandiss package.The ``uncompressed'' and ``compressed'' options are only meaningful ifa PDF file is being produced by ``pdflatex'', in which case theuncompressed option means the resulting file is uncompressed and thecompressed option really means to not set the compression level tonone.  (That is, the compression level will be whatever is thedefault.)The brandiss package has only the online and printed options.  Thesecontrol the format of the signature page, where using the onlineoption formats it for on-line submission and the printed optionformats it for actual signatures.\section{Required Classes and Packages}The brandiss class requires the amsbook class and the brandiss, ifpdf,setspace, geometry, and fancyhdr packages.  The brandiss packagereceives the ``online'' and ``printed'' options, and the amsbookpackage receives all remaining options.The brandiss requires the setspace package.\section{Page Format}The brandiss class formats the page to meet GSAS margin and pagenumbering requirements, and set the PDF compression level to 0 at thebeginning of the document if a PDF file is being produced.  Thegeometry package is used to set the margins as follows:\begin{center}  \begin{tabular}{||c|c||}\hline\hline    Margin & Length \\ \hline\hline    Left & 1.5in \\ \hline    Top & 1in \\ \hline\hline  \end{tabular}  \begin{tabular}{||c|c||}\hline\hline    Margin & Length \\ \hline\hline    Right & 1in \\ \hline    Bottom & 1in \\ \hline\hline  \end{tabular}\end{center}The brandiss class places the header and footer inside the margins andincreases the size of the header and its separation from the main textto accommodate the header.  The fancyhdr package is used to define thefancy page style to have the chapter number and name in the left ofthe header on every page, and to have a page number centered in thefooter of every page.  The ifpdf package is used to detect when a PDFis being produced, and an AtBeginDocument is issued to set the PDFcompress level to 0 if the uncompress option is active.\section{Added Commands and Environments}The brandiss class provides three commands in addition to thoseprovided by the required packages.  The commands and their effectsare:\begin{itemize}\item\textbf{$\backslash$frontmatter} Set double spacing, clear a double  page, set the page style to plain, and the page numbering to roman.\item\textbf{$\backslash$mainmatter} Clear a double page, set the page style  to fancy, and the page numbering to arabic.\item\textbf{$\backslash$backmatter} Clear a double page and set the page  style to plain.\end{itemize}The brandiss package provide multiple commands and environments asfollows.  Many parameters must be set, and are used to includeinformation in the front pages of the dissertation.  The followingcommands lets the user set those parameters.\begin{itemize}\item\textbf{$\backslash$disstitle} The title of the dissertation.\item\textbf{$\backslash$dissauthor} The author.\item\textbf{$\backslash$dissadvisor} The author's advisor.\item\textbf{$\backslash$dissdepartment} The author's department.\item\textbf{$\backslash$dissmonth} The graduation month.\item\textbf{$\backslash$dissyear} The graduation year.\item\textbf{$\backslash$dissdean} The dean of GSAS.\end{itemize}The following command provides transparent access to these values.\begin{itemize}\item\textbf{$\backslash$thediss} Access a parameter  (i.e. ``$\backslash$thediss\{title\}'').\end{itemize}The following commands and environments format the front pages:\begin{itemize}\item\textbf{$\backslash$makedisstitle} This command formats the title  page.\item\textbf{$\backslash$disssignatures} This environment formats the  signature page.  It is list-like and uses the  \textbf{$\backslash$committeemember} command to separate committee  member's names.  The advisor's name is automatically put as the  first entry.  The format depends on the ``online'' and ``printed''  options.\item\textbf{$\backslash$disscopyright} This command formats the  copyright page.\item\textbf{$\backslash$dissdedication} This environment formats the  dedication page.\item\textbf{$\backslash$dissacknowledgments} This environment formats  the acknowledgments page.\item\textbf{$\backslash$dissabstract} This environment formats the  abstract page.\item\textbf{$\backslash$disspreface} This environment formats the  preface page.\end{itemize}\end{document}